Local PCA Shows How Population Structure Differs Along the Genome

### 2016-04-13 writeup/local_pca_paper.tex
added local pca paragraph

Other methods for visualizing population structure are like STRUCTURE, \citep{pritchard2000inference,falush2003inference, falush2007inference,hubisz2009inferring} model-based approach, \citep{yang2012modelbased} maps of heterozygosity \citep{ramachandran2005support}. The term ``local PCA" is also used in some other region for different meanings. \citep{manjon2013diffusion,kambhatla1997dimension,weingessel2000local}

>>>>

Other methods for visualizing population structure are like STRUCTURE,
\citep{pritchard2000inference,falush2003inference,
falush2007inference,hubisz2009inferring} 
model-based approach,
\citep{yang2012modelbased} 
maps of heterozygosity
\citep{ramachandran2005support}.

A number of methods for dimensionality reduction also use a strategy of ``local PCA''
\citep[e.g.][]{manjon2013diffusion,kambhatla1997dimension,weingessel2000local,roweis2000nonlinear},
performing PCA not on the entire dataset but instead on subsets,
providing ``local'' pictures which are then stitched back together to give a global picture.
Our method shares this common thread, but differs somewhat in the context and goals,
and future methods may benefit from this substantial literature \citep[reviewed in][]{vandermaaten2009dimensionality}.
